Regression Analysis of Chicago Crime Volume by Ward using Public School Data

### 2018-11-09 Paper.tex
ready for mid-point

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\graphicspath{ {./Figures/} }
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\urlstyle{same}
\usepackage[font={small,it}]{caption}
\usepackage{fancyvrb}
\title{Regression Analysis of Chicago Crime Volume by Ward using Public School Data}
\author{John D. Bulger, Valparaiso University\thanks{``I have neither given or received, nor have I tolerated other’s use of unauthorized aid."}}
\date{October 5, 2018}

@@

\paragraph{Micro-Level}

@@

\paragraph{Macro-Level}

@@

	The linear model for total crime as a function of the aforementioned four variable exhibits a fairly reasonable level of fit.  It has a $ R^{2} $ value of 0.3154 and a $ \bar{R}^{2} $ of 0.2518.  Both metrics measure overall fit on a scale from 0-1, with $ \bar{R}^{2} $ ``penalizing" for the addition of more variables.  Since this is a multivariate regression, both metrics must be taken into account.  The values for these suggest that this is a model that is indeed indicative of a relationship.  The chosen variables maximize these metrics given the data at hand, since the variables were chosen utilizing a stepwise regression algorithm set to maximize $ \bar{R}^{2} $.
	\par

	A regression's F-value ajfl;fafjasflasjflajlf

@@

@@

	r square and stuff

	A regression's F-value ajfl;fafjasflasjflajlf

	p-value

@@

@@

>>>>

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{pdfpages}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[title]{appendix}
\graphicspath{ {./Figures/} }
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\urlstyle{same}
\usepackage[font={small,it}]{caption}
\usepackage{fancyvrb}
\title{Regression Analysis of Chicago Crime Volume by Ward using Public School Data}
\author{John D. Bulger, Valparaiso University\thanks{``I have neither given or received, nor have I tolerated other’s use of unauthorized aid."}}
\date{October 5, 2018}

@@

\subsection{Micro-Level}

@@

\subsection{Macro-Level}

@@

	The linear model for total crime as a function of the aforementioned four variable exhibits a fairly reasonable level of fit.  It has a $ R^{2} $ value of 0.3154 and a $ \bar{R}^{2} $ of 0.2518.  Both metrics measure overall fit on a scale from 0-1, with $ \bar{R}^{2} $ ``penalizing" for the addition of more variables.  Since this is a multivariate regression, both metrics must be taken into account.  The values for these suggest that this is a model that is indeed indicative of a relationship.  The chosen variables maximize these metrics given the data at hand, since the variables were chosen utilizing a stepwise regression algorithm set to maximize $ \bar{R}^{2} $.

@@

	A regression's F-value is a measure of the model's overall significance when compared to the null hypothesis, which states that the expected coefficients for all of the variables is zero.  While the F-value can range from 0 to an arbitrarily large number, the best measure of its significance is its corresponding p-value.  In this regression model, the p-value was found to be 0.0023.  This is below the established threshold of 0.05 for statistical significance, and the null hypothesis is rejected.

@@

	\paragraph{Theory \& Fit}  In the linear regression for total homicides, the variables all exhibited coefficients with the same indication of relationship.  Therefore, the theory explained and rationalized above extrapolates to this model as well.  The estimate's fit, however, is not as strong as the primary model.  The regression yielded a $ R^{2} $ of 0.2791 and a $ \bar{R}^{2} $ of 0.212.  These metrics are not as high as in the initial regression, suggesting that the regression does not exhibit as good of a fit.  The model has a F-value of 4.16 with a corresponding p-value of 0.0062, which shows the null hypothesis (that all expected variable coefficients should be zero) is rejected.

@@

	As with the prior model, the regression estimate for total homicides was subjected to standard tests for multicollinearity and heteroscedasticity.  Since the same variables were examined, the Variance Inflation Factors, indicators of multicollinearity, remain the same at acceptably low levels.  White's tests was used to produce standard errors for the coefficients, and the resulting adjusted p-values, after adjusting for any heteroscedasticity.  Some change can be seen, but it does not change the p-values by a large margin from where they were originally.
	\begin{center}
	\begin{table}[h]
		\begin{tabular}{ c | c | c | c | c }

@@

\newpage

\begin{appendices}

\section{Linear Regression for Total Crime:  SAS Output}

\includepdf[pages=-]{Figures/linear_total_crime_regression.pdf}

\section{Linear Regression for Total Homicides:  SAS Output}

\includepdf[pages=-]{Figures/linear_total_homicides_regression.pdf}

\end{appendices}
